Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-17 TACAS2018/paper.tex
References

While research on digital control is well
developed~\cite{astrom1997computer}, automated and sound control synthesis
is challenging, particularly when the synthesis objective goes beyond
classical stability.  Recent work~\cite{abate2017automated} described a
method for synthesising safe digital stabilizing controllers for fully
observable LTI plants.  This work differs from the vast majority of existing
approaches in that it explores the continuous space of the system to
synthesise correct by construction minimal digital controllers.  Contrary to
LTL models \todo{citation} that require thousands of states and elaborate algorithms to
implement, these PID-like controllers are represented by a few parameters
and only require a few lines of code, thus reducing the implementation cost
and execution time while remaining resilient to the effects of digitalization.
However,~\cite{abate2017automated}~is restricted to fully observed
systems (i.e., where all the states are known) modelled in discrete time,
and furthemore explores only a limited set of properties that engineers
are interested in. Conversely, 
in most real implementations, the internal state of a plant cannot be
directly measured but rather inferred from its
effect on the output. A plant model that minimises the difference
between its output and the real plant output is called an observer and it is a well known
paradigm in the control literature~\cite{astrom1997computer}.

@@

In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} are soundly discretized in time (see Appendix~\ref{sec:cont_aa}) \todo{or use another paper as reference and remove sec .1?} into
\begin{align}
\label{eq:plant}
\vec{x}_{k+1} = \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
\vec{y}_{k} = \mat{C}_d \vec{x}_k + \mat{D}_d \vec{u}_k
\end{align} 
%
where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
$\mat{A}_d$, $\mat{B}_d$, $\mat{C}_d$ and $\mat{D}_d$ denote the matrices that describe the discretized plant dynamics, whereas $\mat{A}$, $\mat{B}$, $\mat{C}$ and $\mat{D}$ denote the continuous plant dynamics.  In this work we assume $\mat{D}_d=\mat{D}=\mat{0}$. Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
%% We synthesize for requirements over this discrete-time domain. 
%% Later, we will address the issue of variable quantization, 
%% as introduced by the ADC/DAC conversion blocks (Fig.~\ref{fig:digitalsystem}).

@@

%-------------------------------
\subsection{Overapproximating continuous time dynamics using discrete models}
\label{sec:cont_aa}
%-------------------------------
Our plant models derive from the discretization of
continuous time systems.  We therefore seek to establish a sound
overapproximation which does not only encompass the selected discretization,
but any chosen discretization in the time domain.

>>>>

While research on digital control is well
developed~\cite{astrom1997computer}, automated and sound control synthesis
is challenging, particularly when the synthesis objective goes beyond
classical stability.  Recent work~\cite{abate2017automated} described a
method for synthesising safe digital stabilizing controllers for fully
observable LTI plants.  This work differs from the vast majority of existing
approaches in that it explores the continuous space of the system to
synthesise correct by construction minimal digital controllers.  Contrary to
LTL models that require thousands of states and elaborate algorithms to
implement \cite{reissig2017feedback}, these PID-like controllers are represented by a few parameters
and only require a few lines of code, thus reducing the implementation cost
and execution time while remaining resilient to the effects of digitalization.
However,~\cite{abate2017automated}~is restricted to fully observed
systems (i.e., where all the states are known) modelled in discrete time,
and furthemore explores only a limited set of properties that engineers
are interested in. Conversely, 
in most real implementations, the internal state of a plant cannot be
directly measured but rather inferred from its
effect on the output. A plant model that minimises the difference
between its output and the real plant output is called an observer and it is a well known
paradigm in the control literature~\cite{astrom1997computer}.

@@

In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} are soundly discretized in time~\cite{van1978computing,middleton1990digital} (see Appendix~\ref{sec:cont_aa}) into
\begin{align}
\label{eq:plant}
\vec{x}_{k+1} = \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
\vec{y}_{k} = \mat{C}_d \vec{x}_k + \mat{D}_d \vec{u}_k
\end{align} 
%
where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
$\mat{A}_d$, $\mat{B}_d$, $\mat{C}_d$ and $\mat{D}_d$ denote the matrices that describe the discretized plant dynamics, whereas $\mat{A}$, $\mat{B}$, $\mat{C}$ and $\mat{D}$ denote the continuous plant dynamics.  In this work we assume $\mat{D}_d=\mat{D}=\mat{0}$. Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
%% We synthesize for requirements over this discrete-time domain. 
%% Later, we will address the issue of variable quantization, 
%% as introduced by the ADC/DAC conversion blocks (Fig.~\ref{fig:digitalsystem}).

@@

%-------------------------------
\section{Overapproximating continuous time dynamics using discrete models}
\label{sec:cont_aa}
%-------------------------------
Our plant models derive from the discretization of
continuous time systems.  We therefore seek to establish a sound
overapproximation which does not only encompass the selected discretization,
but any chosen discretization in the time domain.
